Music Perception 1: Analysis

### 2022-01-31 experiment-1/analysis/analysis.Rmd
finalise analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

- For additional analysis
(3. Correct answers would be 1) participants pressed "YES" when they listened to teaching performances or 2) participants pressed "NO" when they listened to performing performances.)

@@

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
 for (note in 1:length(ls_legato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
 }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
 for (note in 1:length(ls_staccato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
 }
}
# Forte
for (phrase in 1:length(ls_forte)){
 for (note in 1:length(ls_forte[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
 }
}
# Piano
for (phrase in 1:length(ls_piano)){
 for (note in 1:length(ls_piano[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
 }
}
# assign Subcomponent Change
for (number in change_1){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

@@

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
```
## Dynamics (n.s.)
```{r, echo = TRUE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

# assign Subcomponents
dt_kot$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
   for (note in 1:length(ls_legato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
   for (note in 1:length(ls_staccato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte)){
   for (note in 1:length(ls_forte[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano)){
   for (note in 1:length(ls_piano[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
   }
}
# assign Subcomponent Change
for (number in change_1){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```
## Legato (**)
```{r, echo = TRUE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

# KOT
## Legato (**)
### Estimate
```{r partial-plot-leg, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Legato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Staccato (*)
### Estimate
```{r partial-plot-sta, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Staccato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

# KV
## Forte (*)
### Estimate
```{r partial-plot-for, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Forte", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Piano (n.s.)
### Estimate
```{r partial-plot-pia, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Piano", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

# KV-Diff
## Forte to Piano (n.s.)
### Estimate
```{r partial-plot-ftop, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent2 == "FtoP", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Piano to Forte (***)
### Estimate
```{r partial-plot-ptof, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent2 == "PtoF", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

>>>>

@@

# assign Subcomponents
dt_ioi$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
 for (note in 1:length(ls_legato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
 }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
 for (note in 1:length(ls_staccato[[phrase]])){
   dt_ioi[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
 }
}
# Forte
for (phrase in 1:length(ls_forte)){
 for (note in 1:length(ls_forte[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
 }
}
# Piano
for (phrase in 1:length(ls_piano)){
 for (note in 1:length(ls_piano[[phrase]])){
   dt_ioi[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
 }
}

# assign Subcomponent Change
for (number in change_1){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
 dt_ioi[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
 dt_ioi[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

@@

cor.test(cv[Skill == "articulation"]$Teaching, cv[Skill == "articulation"]$CV, method = "spearman", exact = FALSE)
```

## Dynamics (n.s.)
```{r, echo = TRUE}
# normality check
cv_dyn_norm_teaching <- shapiro.test(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_judge <- shapiro.test(cv[Skill == "dynamics"]$CV)

@@

# assign Subcomponents
dt_kot$Subcomponent <- "NA"
# Legato
for (phrase in 1:length(ls_legato)){
   for (note in 1:length(ls_legato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_legato[[phrase]][note]]$Subcomponent <- "Legato"
   }
}
# Staccato
for (phrase in 1:length(ls_staccato)){
   for (note in 1:length(ls_staccato[[phrase]])){
     dt_kot[Skill == "articulation" & Interval == ls_staccato[[phrase]][note]]$Subcomponent <- "Staccato"
   }
}
# Forte
for (phrase in 1:length(ls_forte)){
   for (note in 1:length(ls_forte[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_forte[[phrase]][note]]$Subcomponent <- "Forte"
   }
}
# Piano
for (phrase in 1:length(ls_piano)){
   for (note in 1:length(ls_piano[[phrase]])){
     dt_kot[Skill == "dynamics" & Interval == ls_piano[[phrase]][note]]$Subcomponent <- "Piano"
   }
}

# assign Subcomponent Change
for (number in change_1){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "LtoS"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "FtoP"
}
for (number in change_2){
   dt_kot[Skill == "articulation" & Interval == number]$Subcomponent <- "StoL"
   dt_kot[Skill == "dynamics" & Interval == number]$Subcomponent <- "PtoF"
}
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

## Legato (**)
```{r, echo = TRUE}
# normality check
kot_leg_norm_teaching <- shapiro.test(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_judge <- shapiro.test(kot_all[Subcomponent == "Legato"]$Mean)

@@

# KOT
## Legato (**)
### Estimate
- partial correlation coefficient between two variables (Teaching vs KOT)

```{r partial-plot-leg, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Legato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Staccato (*)
### Estimate
- partial correlation coefficient between two variables (Teaching vs KOT)

```{r partial-plot-sta, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Staccato", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

# KV
## Forte (*)
### Estimate
- partial correlation coefficient between two variables (Teaching vs KV)

```{r partial-plot-for, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Forte", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Piano (n.s.)
### Estimate
- partial correlation coefficient between two variables (Teaching vs KV)

```{r partial-plot-pia, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent == "Piano", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

# KV-Diff
## Forte to Piano (n.s.)
### Estimate
- partial correlation coefficient between two variables (Teaching vs KVDiff)

```{r partial-plot-ftop, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent2 == "FtoP", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```

@@

## Piano to Forte (***)
### Estimate
- partial correlation coefficient between two (Teaching vs KVDiff)

```{r partial-plot-ptof, echo = FALSE}
# plot
corrplot.mixed(pcor(partial[Subcomponent2 == "PtoF", c("Teaching", "IOI", "KOT", "KV", "KVDiff")])$estimate, diag = c("n"))
```
